\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym} \usepackage[empty]{fullpage} \usepackage{titlesec} \usepackage{marvosym} \usepackage[usenames,dvipsnames]{color} \usepackage{verbatim} \usepackage{enumitem} \usepackage[hidelinks]{hyperref} \usepackage{fancyhdr} \usepackage[english]{babel} \usepackage{tabularx} \usepackage{hyphenat} \usepackage{fontawesome}
\input{glyphtounicode}
\pagestyle{fancy} \fancyhf{} \fancyfoot{} \renewcommand{\headrulewidth}{0pt} \renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.70in} \addtolength{\evensidemargin}{-0.70in} \addtolength{\textwidth}{1.4in} \addtolength{\topmargin}{-0.75in} \addtolength{\textheight}{1in}
\urlstyle{same}
\raggedbottom \raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeEducationHeading}[8]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
		\textit{\small#5} & \textit{\small #6} \\
		\textit{\small#7} & \textit{\small #8} \\
	\end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[2]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeOrganizationHeading}[3]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} \textit{\small #2} & \textit{\small#3}
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%--------------------------------------------------------------------------------------------------------------
\begin{document}

\begin{center}
	\textbf{\Huge \scshape Camron Braden \\ \vspace{2pt} \normalsize IT ANALYST} \\ \vspace{2pt}
	\small \href{tel:901482638}{+1 (901) 482 6318} $|$ \href{mailto:camronrbraden@gmail.com}{CamronRBraden@gmail.com} $|$  \href{https://www.linkedin.com/in/cambraden/}{LinkedIn.com/in/camBraden} $|$ \href{http://github.com/camBraden}{GitHub.com/camBraden} $|$ \href{https://goo.gl/maps/cEZ8epnCLyXyiohs8}{Olive Branch, MS}    
\end{center}

\section{\textbf Skills}
	\resumeSubHeadingListStart
	\small{\item{
		\textbf{Development:}{ SQL, Python, JavaScript, HTML/CSS} \\ \vspace{3pt}
		\textbf{IT Support:}{ Microsoft Windows 10/11 \& Office 365, Apple MacOS, Google Workspace} \\ \vspace{3pt}
		\textbf{Tools:}{  Excel/Google Sheets, Adobe CC, WordPress} \\ \vspace{3pt}
	}}
	\resumeSubHeadingListEnd     

\section{\textbf Certifications}
	\resumeSubHeadingListStart
		\small \resumeOrganizationHeading {CompTIA Network+}{(N10-008)}{07/2023}
		\\ \vspace{7pt}
		\small \resumeOrganizationHeading {CompTIA A+}{(220-1101 \& 220-1102)}{09/2022}
	\resumeSubHeadingListEnd

\section{\textbf Work Experience}
	\resumeSubHeadingListStart
		\resumeSubheading
			{Libertas School of Memphis}{Memphis, TN}
			{Data and SIS (Student Information Systems) Specialist}{09/2022 \textbf{—} 07/2023}
			\resumeItemListStart
				\resumeItem{Managed all student information systems and supported their data transmission to our \textbf{Google BigQuery} data warehouse: PowerSchool SIS, SchoolMint, and ClassTag.}
				\resumeItem{Analyzed and communicated data trends to school administration members by creating dashboards in \textbf{Google Data Studio} and \textbf{Google Sheets} for tracking many data points key to funding various programs: student attendance, state testing scores and growth over time, pre-kindergarten family referrals, etc.}
				\resumeItem{Developed custom software tools for automatically generating family/student facing documents using \textbf{Google AppScript}: report cards, car name tags, etc. These tools replaced subscription software tools that the organization had been using for years.}
				\resumeItem{Administered all software and hardware IT needs for teachers (\textbf{FreshDesk}): \textbf{Google Workspace} admin, \textbf{Apple iPad} support, \textbf{Google Chromebook} repair/distribution, WiFi/network admin via \textbf{Aruba Central}, and \textbf{Konica Minolta Bizhub} printer troubleshooting.}
			\resumeItemListEnd
		\resumeSubheading
			{ALLMemphis}{Memphis, TN/Remote}
			{Associate Technologist}{05/2021 \textbf{—} 07/2022}
			\resumeItemListStart
				\resumeItem{Managed and edited content for our \textbf{WordPress} allmemphis.org website.}
				\resumeItem{QA tested and collected and edited curriculum data for our web app, Ditto Literacy, a portal designed for teachers to quickly generate software-customized curricula for students.}
				\resumeItem{Served as a main contact between ALLMemphis and our contracted software developers.}
				\resumeItem{Edited static documents (\textbf{Adobe Acrobat and Illustrator}; \textbf{Figma}) and videos (\textbf{DaVinci Resolve Studio}) to reflect new marketing/design additions of brochures, worksheets, etc.}
			\resumeItemListEnd
		\resumeSubheading
			{Transnetyx}{Cordova, TN}
			{Technical Services Associate}{03/2021 \textbf{—} 04/2022}
			\resumeItemListStart
				\resumeItem{Provided level 1 help desk support and troubleshooting through \textbf{HappyFox} tickets for more than 250 employees both locally and internationally (remote): created and managed \textbf{Office365} accounts via \textbf{Azure Active Directory}, deployed software to end users via \textbf{Desktop Central}, managed \textbf{Sonitrol} security door key fob access, and repaired/replaced/upgraded staff laptops and desktops.}
				\resumeItem{Assisted with major IT upgrade projects: on-site \textbf{Cisco Meraki} WiFi upgrade, phone system transfer (from \textbf{Shoretel} to \textbf{Windstream/WeConnect}), transitioning on-site physical servers to virtual \textbf{Nutanix} clusters.}
			\resumeItemListEnd
		\resumeSubheading
			{INDEPENDENT CONTRACT}{Remote}
			{Personal Web Design/Development Tutor}{08/2020 \textbf{—} 06/2022}
			\resumeItemListStart
				\resumeItem{Provided instruction to high-school students to create website projects and games \href{https://github.com/Web-Development-Design-Tutoring}{(LINK HERE)}.}
				\resumeItem{Developed weekly curriculum to help students advance their skills with \textbf{HTML/CSS} and \textbf{JavaScript}.}
			\resumeItemListEnd
		\resumeSubheading
			{iD Tech Camps}{Memphis, TN/Remote}
			{Instructor}{05/2019 \textbf{—} 03/2021}
			\resumeItemListStart
				\resumeItem{Provided instruction for Online Private Lessons (Remote) from April 2020 to March 2021. Taught Java, JavaScript, Python, HTML/CSS, and Scratch programming to children aged 8-16 years old with custom curriculum tailored to each student.}
				\resumeItem{Provided instruction for Tech Camps (In-Person) from May to July 2019. Taught Java (Minecraft Mods), JavaScript (BBC micro:bit), and Python (Anki Cozmo) to children aged 9-13 years old.}
			\resumeItemListEnd
	\resumeSubHeadingListEnd

\section{\textbf Education}
	\resumeSubHeadingListStart
		\resumeEducationHeading {Tech901}{Memphis, TN} {\href{https://www.tech901.org/networking}{IT Networking}}{04/2023 — 06/2023} {\href{https://www.tech901.org/data-analytics}{Data Analytics}}{01/2023 — 03/2023} {\href{https://www.tech901.org/foundations}{IT Foundations}}{05/2017 — 06/2017}
		\\ \vspace{9pt}
		\resumeSubheading {University of Memphis}{Memphis, TN}{Computer Science (STANDING JUNIOR with 70+ hours)}{08/2018 — 05/2020}
	\resumeSubHeadingListEnd

\end{document}