\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym} \usepackage[empty]{fullpage} \usepackage{titlesec} \usepackage{marvosym} \usepackage[usenames,dvipsnames]{color} \usepackage{verbatim} \usepackage{enumitem} \usepackage[hidelinks]{hyperref} \usepackage{fancyhdr} \usepackage[english]{babel} \usepackage{tabularx} \usepackage{hyphenat} \usepackage{fontawesome}
\input{glyphtounicode}
\pagestyle{fancy} \fancyhf{} \fancyfoot{} \renewcommand{\headrulewidth}{0pt} \renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in} \addtolength{\evensidemargin}{-0.5in} \addtolength{\textwidth}{1in} \addtolength{\topmargin}{-.5in} \addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom \raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeEducationHeading}[8]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
		\textit{\small#5} & \textit{\small #6} \\
		\textit{\small#7} & \textit{\small #8} \\
	\end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[2]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeOrganizationHeading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{\small #2} \\
		\textit{\small#3}
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
	\textbf{\Huge \scshape Camron Braden} \\ \vspace{1pt}
	\small
	\href{tel:901482638}{+1 (901) 482 6318} $|$ \href{mailto:camronrbraden@gmail.com}{CamronRBraden@gmail.com} $|$  \href{https://www.linkedin.com/in/cambraden/}{LinkedIn.com/in/camBraden} $|$ \href{http://github.com/camBraden}{GitHub.com/camBraden} $|$ \href{https://goo.gl/maps/cEZ8epnCLyXyiohs8}{Olive Branch, MS}    
\end{center}

\section{Work Experience}
	\resumeSubHeadingListStart
		\resumeSubheading
			{Libertas School of Memphis}{Memphis, TN}
			{Data and SIS (Student Information Systems) Specialist}{September 2022 \textbf{—}July 2023}
			\resumeItemListStart
				\resumeItem{Managed all student information systems and support their data transmission to our data warehouse (Google BigQuery): PowerSchool SIS, SchoolMint, and ClassTag.}
				\resumeItem{Analyzed and communicated data trends to school administration members by creating dashboards for tracking many data points key to funding various programs (Google Data Studio \& Google Sheets): student attendance, state testing scores and growth over time, pre-kindergarten family referrals, etc.}
				\resumeItem{Developed custom software tools for creating family/student facing documents (Google AppScript): report cards, car name tags. These tools replaced subscription software tools that the organization had been using for years.}
				\resumeItem{Administer all software and hardware IT needs for teachers (FreshDesk): Google Workspace admin, Chromebook repair/distribution, WiFi/network admin (Aruba Central), and printer troubleshooting (Konica Minolta Bizhub)}
			\resumeItemListEnd

		\resumeSubheading
			{ALLMemphis}{Memphis, TN/Remote}
			{Associate Technologist}{May 2021 \textbf{—} July 2022}
			\resumeItemListStart
				\resumeItem{Managed and edited content for our WordPress allmemphis.org website.}
				\resumeItem{QA tested and collected and edited curriculum data for our web app, Ditto Literacy, a portal designed for teachers to quickly generate software-customized curricula for students.}
				\resumeItem{Served as a main contact between ALLMemphis and our contracted software developers.}
				\resumeItem{Edited static documents (Adobe Acrobat and Illustrator; Figma) and videos (iMovie and DaVinci Resolve) to reflect new marketing/design additions of brochures, worksheets, etc.}
			\resumeItemListEnd

		\resumeSubheading
			{Transnetyx}{Cordova, TN}
			{Technical Services Associate}{March 2021 \textbf{—} April 2022}
			\resumeItemListStart
				\resumeItem{Provided level 1 help desk support and troubleshooting through HappyFox tickets for more than 250 employees both locally and internationally (remote): created and managed Office365 accounts (Azure Active Directory), deployed software to end users (Desktop Central), managed security door key fob access (Sonitrol), and repaired/replaced/upgraded staff laptops and desktops.}
				\resumeItem{Assisted with major IT upgrade projects: on-site WiFi upgrade (Cisco Meraki), phone system transfer (from Shoretel to Windstream/WeConnect), transitioning on-site physical servers to virtual Nutanix clusters.}
			\resumeItemListEnd

		\resumeSubheading
			{[SELF EMPLOYED]}{Remote}
			{Personal Web Design/Development Tutor}{August 2020 \textbf{—} June 2022}
			\resumeItemListStart
				\resumeItem{Provided instruction to high-school students to create website projects and games \href{https://github.com/Web-Development-Design-Tutoring}{(LINK HERE)}.}
				\resumeItem{Developed weekly curriculum to help students advance their skills with HTML/CSS and JavaScript.}
			\resumeItemListEnd

		\resumeSubheading
			{iD Tech Camps}{Memphis, TN/Remote}
			{Instructor}{May 2019 \textbf{—} March 2021}
			\resumeItemListStart
				\resumeItem{Provided instruction for Online Private Lessons (Remote) from April 2020 to March 2021. Taught Java, JavaScript, Python, HTML/CSS, and Scratch programming to children aged 8-16 years old with custom curriculum tailored to each student.}
				\resumeItem{Provided instruction for Tech Camps (In-Person) from May to July 2019. Taught Java (Minecraft Mods), JavaScript (BBC micro:bit), and Python (Anki Cozmo) to children aged 9-13 years old.}
			\resumeItemListEnd

	\resumeSubHeadingListEnd

\section{Certifications}
	\resumeSubHeadingListStart

		\resumeOrganizationHeading {CompTIA Network+}{July 2023}{Tech901 IT Networking}

		\resumeOrganizationHeading {CompTIA A+}{September 2022}{Tech901 IT Foundations}

	\resumeSubHeadingListEnd

\section{Education}
	\resumeSubHeadingListStart
		\resumeEducationHeading {Tech901}{Memphis, TN} {IT Networking}{April \textbf{—} June 2023} {Data Analytics}{January \textbf{—} March 2023} {IT Foundations}{May \textbf{—} June 2017} \\ \vspace{7pt}
		\resumeSubheading {University of Memphis}{Memphis, TN}{Computer Science [STANDING JUNIOR with 70+ hours]}{August 2018 \textbf{—} May 2020}\resumeSubHeadingListEnd

\section{Skills}
	\resumeSubHeadingListStart
		\small{\item{
        \textbf{Development: }{SQL, Python, JavaScript, HTML/CSS} \\ \vspace{3pt}
        
        \textbf{IT Support: }{Windows 10/11, Office 365, MacOS, Google Workspace} \\ \vspace{3pt}
        
        \textbf{Tools: }{Excel/Google Sheets, Adobe CC, WordPress}

 }}
\resumeSubHeadingListEnd

\end{document}